Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-22 paper/paper.tex
Update authors

\author {\textbf{Nombre Apellidos1,$^1$} \textbf{Nombre Apellidos2$^2$}\\
$^1$Universidad o lugar de trabajo\\
$^2$Universidad o lugar de trabajo\\
Información de contacto\\
}

>>>>

\author {
  \textbf{Alejandro Piad-Morffis,$^{1,*}$},
  \textbf{Suilan Estevez-Velarde$^1$},
  \textbf{Yoan Gutierrez$^{2,3}$}\\
  \textbf{Yudivian Almeida-Cruz$^1$},
  \textbf{Andrés Montoyo$^{2,3}$},
  \textbf{Rafael Muñoz$^{2,3}$}\\
$^1$School of Math and Computer Science, University of Havana, Cuba\\
\texttt{\{apiad,sestevez,yudy\}@matcom.uh.cu}\\
$^2$University Institute for Computer Research, IIUI, University of Alicante, Spain\\
$^2$Department of Language and Computing Systems, University of Alicante, Spain\\
\texttt{\{ygutierrez,montoyo,rafael\}@dlsi.ua.es}\\
}
